---
title: "Summary listing from Jamaica"
author: "Michael Rahija"
date: "April 12, 2016"
output: pdf_document
---

```{r, echo = FALSE, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
# tabulate listing data
library(memisc)
library(dplyr)
library(reshape)

```

# Overview of listing data collected

## Number of listed farmers, and parcels by EA
```{r, echo = FALSE}
#set wd
setwd("~/Dropbox/CROP/Jamaica/cropJam")
data.dir <- "~/Dropbox/CROP/Jamaica/data_listing"


#create data sets
source("R/createDataset.R")
master <- createDataset()

###I think interviews a153adf0d43e472794211be60d15cbcd and 940281e1c43d41cb84dd4dbf9b2b26dd
###have data entry errors b/c there are instances when parcelId != parcel_list

#clean data set
source("R/cleanDataset.R")
master <- cleanDataset(df = master)

tab <- master %>%
          group_by(ea) %>%
          summarize(listedFarmers = length(unique(qId)),
                    listedParcels = n())

knitr::kable(tab, caption = paste("Total interviews = ", sum(tab$listedFarmers),
                                  "\n", 
                                  "Total parcels = ", sum(tab$listedParcels)))

```


## Number of parcels containing sweet potato, irish potato, yellow yam, onion, other crops, and mixed crops by enumeration area. 


```{r, echo=FALSE}
#create variable for # of crops on a parcel
master$sweetPotato[master$sweetPotato > 0] <- TRUE
master$irishPotato[master$irishPotato > 0] <- TRUE
master$yellowYam[master$yellowYam > 0] <- TRUE
master$onion[master$onion > 0] <- TRUE
master$otherCrop[master$otherCrop > 0] <- TRUE

master$noCrops <- master$sweetPotato +
                      master$irishPotato +
                      master$yellowYam +
                      master$onion +
                      master$otherCrop 

tab <- master %>%
          group_by(ea) %>%
          summarize(sweetPotato = sum(sweetPotato, rm.na = TRUE),
                    irishPotato = sum(irishPotato, na.rm = TRUE),
                    yellowYam = sum(yellowYam, na.rm = TRUE), 
                    onion = sum(onion, na.rm = TRUE),
                    otherCrop = sum(otherCrop, na.rm = TRUE),
                    numberMixed = sum(noCrops > 1, na.rm = TRUE))
                      
knitr::kable(tab)


# tab <- master %>%
#         group_by(Other_rop)%>%
#         summarize(Other = n())
# as.data.frame(tab)
        
```

# Paradata analysis - doesn't include first version questionnaire

## Number of interviews by interviewer and median duration of interview in seconds
*Notably, some interviewers didn't enter the data in tablet at time of collection. Instead, they wrote the responses on paper, and transcribed in tablet. It would be interesting to know which interviews used which method to compare the duration.
```{r, echo=FALSE}
para <- read.table(paste0(data.dir,"/","interview_actions.tab"),
                         sep = "\t",
                         stringsAsFactors = FALSE,
                         header = TRUE)

source("R/interviewTable.R")
para <- interviewTable(para, 
                       format.time = FALSE)

interviews <- para %>%
                group_by(Interviewer) %>%
                summarize(medianDurationinSeconds = median(as.numeric(Duration), 
                                                  na.rm = TRUE),
                          numberOfInterviewsCompleted = n())
                
knitr::kable(interviews)
````
